Language-Based Low-Level MPC Security: $\metaprot$ to $\minifed$

### 2024-05-13 ppdp24/examples.tex
checkpoint

\section{Examples}
\label{section-examples}

@@

\begin{definition}
  We write $\condsep{\pmf}{X_1}{X_2}{X_3}$ iff for all
  $\store' \in \mems(X_1)$ and $\store \in \mems(X_2 \cup X_3)$
  and letting $X = X_1 \cup X_2 \cup X_3$ we have:
  $$\condd{\pmf}{X}{\store'}(\store) =
  \condd{\pmf}{X}{\store'}(\store_{X_2}) *
  \condd{\pmf}{X}{\store'}(\store_{X_3})$$
  We write $\conddetx{\pmf}{X_1}{X_2}$ iff for all
  $\store' \in \mems(X_1)$ there exists 
  $\store \in \mems(X_2)$ such that
  $\condd{\pmf}{X_1 \cup X_2}{\store'}(\store) = 1$.
\end{definition}

@@

\begin{lemma}
  Given:
  \begin{mathpar}
    \condsep{\pmf}{X_1}{X_2}{X_3}

    \condp{\pmf}{X_1}{\detx{X_2}}

    \condp{\pmf}{X_2}{\detx{X_4}}
  \end{mathpar}
    Then $\condsep{\pmf}{X_1}{X_4}{X_3}$.
\end{lemma}

\begin{lemma}
  $$ (\varnothing,e) \redxs (\prog,\decodegmw(E[\mesg{z}])) $$
  $$\iov(\prog) = S \cup M$$
  $$\condsep{\progtt(\prog)}{S}{\{\macgv{\mesg{z}}\}}{(M_C \cup \{ \elab{\mesg{z}}{1}, \elab{\mesg{z}}{2} \})}$$
  $$\conddetx{\progtt(\prog)}{S}{\{\macgv{\mesg{z}}\}}$$
\end{lemma}

\begin{mathpar}
  \condsep{\progtt(\prog_1)}{S^1}{\{ \macgv{\mesg{x}} \}}{(M^1_C \cup \{ \elab{\mesg{x}}{1}, \elab{\mesg{x}}{2} \})}

@@

  \condsep{\progtt(\prog_3)}{S^1 \cup S^2}{\{ \macgv{\mesg{z}} \}}{(M^1_C \cup M^2_C \cup \{ \elab{\mesg{x}}{2}, \elab{\mesg{y}}{2}, \elab{\mesg{z}}{1}, \elab{\mesg{z}}{2} \})}
\end{mathpar}

>>>>

\section{Examples and Proof Methods}
\label{section-examples}

@@

\begin{definition}[Conditional Separation]
  We write $\condsep{\pmf}{X_1}{X_2}{X_3}$ iff for all
  $\store' \in \mems(X_1)$ and $\store \in \mems(X_2 \cup X_3)$
  and letting $X = X_1 \cup X_2 \cup X_3$ we have:
  $$\condd{\pmf}{X}{\store'}(\store) =
  \condd{\pmf}{X}{\store'}(\store_{X_2}) *
  \condd{\pmf}{X}{\store'}(\store_{X_3})$$
\end{definition}

\begin{definition}[Conditional Determinism]  
  We write $\conddetx{\pmf}{X_1}{X_2}$ iff for all
  $\store' \in \mems(X_1)$ there exists 
  $\store \in \mems(X_2)$ such that
  $\condd{\pmf}{X_1 \cup X_2}{\store'}(\store) = 1$.
\end{definition}

\begin{lemma}
  \label{lemma-gmwinvariant}
  $$ (\varnothing,e) \redxs (\prog,\decodegmw(E[\mesg{z}])) $$
  $$\iov(\prog) = S \cup M$$
  $$\condsep{\progtt(\prog)}{S}{\{\macgv{\mesg{z}}\}}{(M_C \cup \{ \elab{\mesg{z}}{1}, \elab{\mesg{z}}{2} \})}$$
  $$\conddetx{\progtt(\prog)}{S}{\{\macgv{\mesg{z}}\}}$$
\end{lemma}

@@

\begin{lemma}
  Given $\condsep{\pmf}{X_1}{X_2}{X_3}$ and $\condp{\pmf}{X_1}{\detx{X_2}}$ and $\condp{\pmf}{X_2}{\detx{X_4}}$,
%  \begin{mathpar}
%    \condsep{\pmf}{X_1}{X_2}{X_3}
%    
%    \condp{\pmf}{X_1}{\detx{X_2}}
%
%    \condp{\pmf}{X_2}{\detx{X_4}}
%  \end{mathpar}
    then $\condsep{\pmf}{X_1}{X_4}{X_3}$.
\end{lemma}

\begin{proof}[Proof of Lemma \ref{lemma-gmwinvariant}]
\begin{mathpar}
  \condsep{\progtt(\prog_1)}{S^1}{\{ \macgv{\mesg{x}} \}}{(M^1_C \cup \{ \elab{\mesg{x}}{1}, \elab{\mesg{x}}{2} \})}

@@

  \condsep{\progtt(\prog_3)}{S^1 \cup S^2}{\{ \macgv{\mesg{z}} \}}{(M^1_C \cup M^2_C \cup \{ \elab{\mesg{x}}{2}, \elab{\mesg{y}}{2}, \elab{\mesg{z}}{1}, \elab{\mesg{z}}{2} \})}
\end{mathpar}
\end{proof}
